### 2023-09-11 3.Design/activation.tex
Changed circuit's ref

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in \cref{fig:afCircuit}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in \cref{tab:afPar}.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{activation/afCircuit}
  \caption{Activation functions circuit}
  \label{fig:afCircuit}
\end{figure}

@@

Note that the actual output of the circuit in \cref{fig:afCircuit} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the

>>>>

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in \cref{circt:af}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in \cref{tab:afPar}.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{activation/afCircuit}
  \caption{Activation functions circuit}
  \label{circt:af}
\end{figure}

@@

Note that the actual output of the circuit in \cref{circt:af} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the

### 2023-09-11 3.Design/inverter.tex
onchip area begin + timediagram for memcell
Worked on xbar + new package for refs + cleaning repo
Changed circuit's ref

\begin{figure}[H]
  \centering
  \hspace*{2.5cm}
  \subfloat[Inverter's circuit]{\label{fig:invCircuit}\includesvg[height=3cm]{inverter/invCircuit}}%
  \hfill
  \subfloat[Inverter's symbol]{\label{fig:invSymbol}\includesvg[height=2.5cm]{inverter/invSymbol}}%
  \hspace*{1.5cm}
  \caption{}
  \label{fig:inv}
\end{figure}

Figure \ref{fig:inv} combines the circuit and the symbol of the inverter used in this thesis.

>>>>

\begin{figure}[H]
  \centering
  \hspace*{2.5cm}
  \subfloat[Inverter's circuit]{\label{circt:inv}\includesvg[height=3cm]{inverter/invCircuit}}%
  \hfill
  \subfloat[Inverter's symbol]{\label{fig:invSymbol}\includesvg[height=2.5cm]{inverter/invSymbol}}%
  \hspace*{1.5cm}
  \caption{}
  \label{fig:inv}
\end{figure}

\Cref{fig:inv} combines the circuit and the symbol of the inverter used in this thesis.

The approximate onChip area for the inverter is :
\begin{equation}
  A_{inv}=2\cdot A_{CMOS}
\end{equation}

With $A_{CMOS}= w\cdot l$ TODO check w et l
